Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-05 Manuscript Analyses/manuscript_analysis.Rmd
Cleaning code and formatting rmd

Pretest and posttest intelligibility, as measured by percent words correct, for each of the two speaker conditions are presented below. On average, pretest intelligibility for AM1 was lower than PDM10. However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10. A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p < .001, d = 1.01).

@@

@@

@@

@@

```{r}
t_for_diff(mods2)
```

@@

# Mergining initial model summaries together
initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)

@@

@@

@@

@@

@@

>>>>

Pretest and posttest intelligibility, as measured by percent words correct, for each of the two speaker conditions are presented below. On average, pretest intelligibility for AM1 was lower than PDM10. However, the listener's who were trained with AM1, on average, had greater intelligibility gains at posttest compared to the listener's trained with PDM10. A repeated measures ANOVA was conducted on the pretest-posttest change for the AM1 was significant (F(1,32) = 103.69, p \< .001, d = 1.01).

@@

Two elastic net models were conducted to evaluate the predictive relationship between the cognitive measures on pretest (initial) intelligibility: A model containing only the main effects of the cognitive measures (i.e. the main effects model) and another model that contains the main effects and all two-way interactions (i.e. the interaction model). The cross-validated R-squared and RMSE values are not significantly different between these two models.

The relative variable importance for the models are shown in the figure below. The interaction between episodic (picture sequence) memory and words in noise hearing threshold, the main effect of words in noise threshold, the interaction between working memory and receptive vocabulary, and the interaction between working memory and processing speed were the most important variables for the AM1 initial intelligibility models.

@@

Plotting the interaction effects for the AM1 initial intelligibility models.

@@

Like for AM1, two elastic net models were used to model the predictive relationship between the listener cognitive measures and pretest intelligibility for PDM10: a main effects model and an interaction model. The difference in R-square and RMSE is not significantly different between the two models. However, the R-squared value is higher for the main effects model, indicating a better fit to the data.

The important variables for the PDM10 models is shown below. The interaction between receptive vocabulary and processing speed, the main efffect of words in noise hearing threshold, the interaction between inhibitory control and words in noise hearing threshold, and the interaction between working memory and processing speed were the most important variables in the models (in that order).

@@

```{r, warning = F, message = F}
t_for_diff(mods2)
```

Plotting the interaction effects for the AM1 initial intelligibility models.

@@

# Merging initial model summaries together
initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)

@@

Two elastic net models were used to model the relationship between the listener cognitive measures and intelligibility improvement (controlling for pretest intelligibility) for AM1: the main effects only model and the model with interactions. Based on the R-squared values, the main effects model is better than the interaction model (this difference approached significance).

The relative importance of the model variables are shown in the figure below.

@@

```{r warning = F, message = F}

@@

Plotting the interaction effects for intelligibility improvement models for AM1.

@@

Two elastic net models were used to model the relationships between listener cognition measures and intelligibility improvement (controlling for pretest intelligibility) for PDM10. There is not a significant difference between the R-squared values for the two models.

The relative importance of the model variables is shown in the figure below.

@@

Plotting the interaction effects for the intelligibility improvement models for PDM10.
